### 2017-04-28 sec-conclusion.tex
Future work: emphasize comparative analysis opportunities.

Specifically, our model can be used to produce an ordered list of latent states for each
student over time. Given these labeled sequences, we could correlate
course-wide drifts in these latent states with events in a course. For
example, we might be able to automatically discover difficult or confusing
parts of a course by noticing spikes in the distribution of students over
latent states over time.

>>>>

Our model can empower many new comparative analyses. For example, we could
now look at how behavior patterns change between different offerings of
the same MOOC to understand how changes in course structure or materials
influences student behavior. Individual students can now also be compared
against each other or against groups. For example, by decoding the latent
state sequences for each student, we can measure how ``surprising'' their
latent state transition sequence is relative to the average we would expect
according to the model, or to the average ``perfect'' student, etc. We can
now investigate how certain behavioral patterns correlate with properties
of a student (e.g., demographics, prior aptitude, etc.). After decoding the
students' latent state sequences, we could also correlate course-wide
drifts in these latent states with events in a course. For example, we
might be able to automatically discover difficult or confusing parts of a
course by noticing spikes in the distribution of students over latent
states over time.
